Making Sequential Programs Deterministic

### 2019-04-05 experiments.tex
deflaker nutz

Four of the seven flaky tests (two in \<achilles>, one each in \<jackrabbit-oak> and \<togglz>)
were caused by a race condition, which \theDeterminismChecker
cannot detect.  (This is a strength of DeFlaker over \theDeterminismChecker.)
We were unable to build \<togglz> and \<nutz> which had one flakiness issue each.
However, we extracted the source code causing the flakiness in \<togglz> into a test case 
after looking at the issue on Github. This bug was caused by a copy method that iterated over
an \<OrderNonDet Set> and expected it to be deterministic. \TheDeterminismChecker correctly flagged
an error in the loop that iterated over the \<Set>.
\TheDeterminismChecker was able to find the source of flakiness in \<checkstyle>. This bug was in a test
case that treated an array returned by \<Class.getDeclaredConstructors()>
as deterministic.

>>>>

Four of the seven flaky tests (two in \<achilles>, one each in \<jackrabbit-oak> and \<togglz>)
were caused by a race condition, which \theDeterminismChecker
cannot detect.  (This is a strength of DeFlaker over \theDeterminismChecker.)
We were unable to build \<togglz> and \<nutz> which had one flakiness issue each.
However, we extracted the source code causing the flakiness in these repositories into test cases
after looking at the corresponding issues on Github. The bug in \<togglz> was caused by a copy method that iterated over
an \<OrderNonDet Set> and expected it to be deterministic. \TheDeterminismChecker correctly flagged
an error in the loop that iterated over the \<Set>.
The flakiness in \<nutz> was a result of printing a response received over http.
Since network operations are nondeterministic, we annotated the method in \<nutz> that
returns this response as \<NonDet> which lead \TheDeterminismChecker to report an error at the print statement. 
\TheDeterminismChecker was able to find the source of flakiness in \<checkstyle>. This bug was in a test
case that treated an array returned by \<Class.getDeclaredConstructors()>
as deterministic.
